Learning constraints in tabular data

### 2016-05-11 Paper/ECAI/tabular.tex

@@

\paragraph{Future work}
There are multiple directions for future work on this topic.
The system would be easier to use in an interactive setting where users can easily receive and provide feedback.
Moreover, the system can be adapted to produce less redundant constraints through the use of heuristic filtering.

Currently, the system only learns single constraints, however, extending it to nested constraints would allow more expressive concepts to be learned.
This shift would bring the approach in line with programming by example.

>>>>

\paragraph{Application specific system extension}
\sergey{Explain here, how the system can be extended with a new constraints like vr = floor(v), float(v), int(vr), len(v)=len(vr), v,vr are single vectors}

\begin{equation}
  \forall i{:}~ v_r[i] \leq v[i] < v_r[i] + 0.5
  \label{eq:floor_extension}
\end{equation}

@@

\paragraph{Future work}
There are multiple directions for future work on this topic.
Integrating the system in an interactive setting would offer users the possibility to easily receive and provide feedback.
Moreover, the system can be adapted to deal with additional types produce less redundant constraints through the use of (heuristic) filtering or post-processing.

Currently, the system only learns single constraints, however, extending our approach to nested constraints would allow more expressive concepts to be learned.
This shift would bring the approach in line with programming by example.
